Star-galaxy Classification Using Deep Convolutional Neural Networks

### 2016-08-12 paper/main.tex
[issue 2.22] add probability thresholds

% Enter the current year, for the copyright statements etc.
\pubyear{2015}

@@

@@

Deep learning is a rapidly developing field, and recent developments include
improved network architectures.
For future work, we plan to train more ConvNet variants, such as the
Inception Module~\citep{szegedy2015going} and Residual Network~\citep{he2015deep}.
To improve the predictive performance,
we have combined the predictions of different models across multiple
transformations of the input images (Section~\ref{sec:bmc}).
To further improve the performance, we could also train several networks
with different architectures and combine the models.
For example, the winning solution of \cite{dieleman2015rotation}
for the Galaxy Zoo challenge was based on a ConvNet model,
and it required averaging many sets of predictions from models with different
neural network architectures.

>>>>

% Enter the current year, for the copyright statements etc.
\pubyear{2016}

@@

\changed{
Note that $p_{g}(c_g=0.96)$ and $c_{s}(p_s=0.97)$ require adjusting
threshold values (\ie probability cuts), while other metrics do not.
To obtain a galaxy completeness of $c_g=0.96$, we choose the threshold values
0.9972, 0.9963, and 0.9927 for ConvNet, TPC${}_{\rmn{morph}}$, TPC${}_{\rmn{phot}}$,
respectively;
for star purity $p_s=0.97$, we choose 0.6990, 0.5297, and 0.8570 for
ConvNet, TPC${}_{\rmn{morph}}$, TPC${}_{\rmn{phot}}$, respectively.
In Table ? and ?, we present example.
}

@@

Deep learning is a rapidly developing field, and recent developments include
improved network architectures.
For future work, we plan to train more ConvNet variants, such as the
Inception Module~\citep{szegedy2015going} and Residual Network~\citep{he2015deep}.
To improve the predictive performance,
we have combined the predictions of different models across multiple
transformations of the input images (Section~\ref{sec:bmc}).
To further improve the performance, we could also train several networks
with different architectures and combine the models.
For example, the winning solution of \cite{dieleman2015rotation}
for the Galaxy Zoo challenge was based on a ConvNet model,
and it required averaging many sets of predictions from models with different
neural network architectures.
\changed{
Futhermore, future work could compare the performance of other deep learning
variants, such as deep belief networks~\citep{hinton2006fast},
deep Boltzmann machines~\citep{salakhutdinov2009deep}, or
multilayer perceptrons~\citep{wasserman1988neural}.
}
